Article title

### 2017-08-03 paper-webserver.tex
ADD: outline for materials and methods
ADD: new first draft of first para

\begin{abstract}
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text.
\end{abstract}

@@

@@

% potential of WGS
WGS uses the entire genetic content of an organism, and as such can be used to evaluate the spread of outbreaks with better resolution and context than traditional methods \cite{ronholm2016navigating}.
However, while these WGS-based methods can fully examine the underlying genetics, the expressed phenotype is more difficult to predict.
For example, predictions involving reference databases are only as good as the databases themselves.
Additionally, the cost of developing, approving, and transforming existing workflows from wet-lab to sequence prediction approaches in time consuming and expensive \cite{koser2012routine}.

@@

% Superphy
We have previously developed Superphy \cite{whiteside2016superphy}, an online platform targeting \textit{E. coli}, which provided pre-computed, predictive genomic analyses for determining Shiga toxin subtype, AMR gene profiles, the presence of known virulence factors, and provides predictive biomarkers, both the presence / absence of genomic regions and single nucleotide variants, for bacterial sub-groups based on metadata such as serotype, host source, or location.
While this tool has been useful for the thousands of pre-computed genomes in its database, the current pace of genome sequencing requires real-time predictive genomic analyses of tens of thousands of genomes, and the long term storage and referencing of these results, something that the original SuperPhy platform was incapable of.

@@

\section{MATERIALS AND METHODS}
We designed Spfy's front-end following the Material Design standards \url{https://material.io/}, released by Google.
The user interface is implemented with the React JavaScript library \url{https://facebook.github.io/react/}, by Facebook, as a single-page application to allow efficient data-flow without reloading the website.
Everything is compartmentalized within separate Docker containers where the front-end is networked, through Docker-Compose, to the back-end webserver.

@@

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text{}. Text.
Text \cite{1}.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
\begin{align*}
&\mathrm{Ascorbate} + \mathrm{EDTA} \cdot \mathrm{Fe}^{3+} \to
\hbox{Oxidized ascorbate}
\\
&\mathrm{EDTA} \cdot \mathrm{Fe}^{2+} + \mathrm{H}_2
\mathrm{O}_2 \to
\mathrm{EDTA} \cdot \mathrm{Fe}^{3+} + \cdot
\mathrm{OH} + \mathrm{OH}^-
\end{align*}
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
% **************************************************************
% Keep this command to avoid text of first page running into the
% first page footnotes
\enlargethispage{-65.1pt}
% **************************************************************

Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text.
Text \cite{2,3}.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text.

Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text. Text. Text. Text.
Text. Text. Text. Text. Text. Text. Text. Text.
Text \cite{4}.

\section{MATERIALS AND METHODS}

>>>>

\begin{abstract}

\end{abstract}

@@

% 1. brief: WGS is standard
Whole genome sequencing (WGS) uses the entire genetic content of an organism, and is the new standard for bacterial surveillance \cite{ronholm2016navigating,lytsy2017time}, research into disease \cite{wang2014whole,yuen2015whole}, and clinical diagnoses \cite{willig2015whole,dewey2014clinical}.
% 2. Big Problem: but tools are for individual analysis
Targeted software, such as the Resistance Gene Identifier (RGI) \cite{mcarthur2013comprehensive} for antimicrobial resistance (AMR) gene prediction, Prokka for bacterial genome annotation \cite{doi:10.1093/bioinformatics/btu153}, and integrated platforms, such as the Bacterium Analysis Pipeline (BAP) \cite{thomsen2016bacterial} and the Integrated Rapid Infectious Disease Analysis (IRIDA) project \url{http://www.irida.ca/}, all leverage WGS data.
For bioinformatics software to reach true "big-data" goals, analyses modules must run in real-time and results must be integrated.
% 3. 100,000 genomes, (lookup number for Enterobase, GenBank), how do we run analysis on it
WGS generates data at a break-neck speed; for \textit{Escherichia coli} alone, the public genome databases EnteroBase \url{https://enterobase.warwick.ac.uk/} and GenBank \cite{doi:10.1093/nar/gks1195} have 60,206 and 2,779,008 sequences uploaded, respectively.
Typical bioinformatics software, such as RGI and Prokka, take single files as input, and integrated platforms, such as BAP and IRIDA, build workflows linking different analyses modules.
BAP and IRIDA begin to solve "big-data" challenges by offering a hosted solution which computes results in real-time, and parallelizes analyses across computing resources.
For WGS to further benefit surveillance, research, and clinical fields, analyses results should also be integrated and searchable; storage of results would avoid recomputation, persist data, and allow references to old analyses. \par

% 1. Our specific problem, previous work
We've attempted to build big-data platforms which address both real-time analyses and integrated storage of results. We have previously developed Superphy \cite{whiteside2016superphy}, an online predictive genomics platform targeting \textit{E. coli}.

@@

% potential of WGS
, and as such can be used to evaluate the spread of outbreaks with better resolution and context than traditional methods \cite{ronholm2016navigating}.
However, while these WGS-based methods can fully examine the underlying genetics, the expressed phenotype is more difficult to predict.
For example, predictions involving reference databases are only as good as the databases themselves.
Additionally, the cost of developing, approving, and transforming existing workflows from wet-lab to sequence prediction approaches in time consuming and expensive \cite{koser2012routine}.

@@

% Superphy
, which provided pre-computed, predictive genomic analyses for determining Shiga toxin subtype, AMR gene profiles, the presence of known virulence factors, and provides predictive biomarkers, both the presence / absence of genomic regions and single nucleotide variants, for bacterial sub-groups based on metadata such as serotype, host source, or location.
While this tool has been useful for the thousands of pre-computed genomes in its database, the current pace of genome sequencing requires real-time predictive genomic analyses of tens of thousands of genomes, and the long term storage and referencing of these results, something that the original SuperPhy platform was incapable of.

@@

% **************************************************************
% Keep this command to avoid text of first page running into the
% first page footnotes
\enlargethispage{-65.1pt}
% **************************************************************

\section{MATERIALS AND METHODS}
% outline
% para
% problem: predictive analylitcs in minutes - sol'n: RQ
%	related: packaging of modules in conda
% para (probably 2 paras)
% problem: distribute tasks & automate installation - sol'n: docker
% para(probably 2 for graphs)
% problem: storage up 10,000+ genomes - sol'n: graph database
% para
% problem: responsive ui that's easy to navigate - sol'n: react & material design
% shortpara
% problem: CI/testing - sol'n Github, TravisCI, Pytest

We designed Spfy's front-end following the Material Design standards \url{https://material.io/}, released by Google.
The user interface is implemented with the React JavaScript library \url{https://facebook.github.io/react/}, by Facebook, as a single-page application to allow efficient data-flow without reloading the website.
Everything is compartmentalized within separate Docker containers where the front-end is networked, through Docker-Compose, to the back-end webserver.

@@
